Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-04 SupportingInformation.Rmd
Update SupportingInformation.Rmd
removing skewness results for all sp : aphids count, ff and plankton

 The Great Miami Wetland Mitigation Bank  was at $36^{\circ}46^{'}51^{''}$ N, $84^{\circ}20^{'}26^{''}$ W) in Trotwood, Montgomery County, Ohio. Additional information on the history of the site and soil types is detailed in @Jarecke2016. Briefly, the closed static flux chamber method was used [@Holland1999] to measure $CH_{4}$ fluxes at 28 locations across a hydrologic gradient (upland to seasonal wetland) at daily to weekly interval from September 2015 to September 2016. **See and Smyth et al, pending for
additional details???** on greenhouse gas flux methods for this site. We considered 13 locations that had at least 50 dates data.

@@

<!--Following 3 chunks examine the consequence of non-Normal copula atructure on skewness using aphid count, firstflight for 20 sp.
and plankton count data for 22 sp. : these results are currently not showin in either main text or suppmat-->
```{r skewness_aphidcount_allsp_plot, echo=F, results="hide", cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

# For sp =1, sp=4 and sp=6 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite
# also it can't handle ties for "kendall" and code crashes
# you can see those msg by deleting results="hide" and warning=F option in r chunk

numsurrog<-10000

splist<-c(1:20)
skw_aphid_count_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_spearman.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_spearman$realskw[i]<-ans$realskw
  skw_aphid_count_spearman$p_left[i]<-p_left
  skw_aphid_count_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_spearman,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_spearman.RDS")

#skw_aphid_count_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
#colnames(skw_aphid_count_kendall)<-c("realskw","p_left","p_right")
#rownames(skw_aphid_count_kendall)<-paste("sp",splist,sep="")
#pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_kendall.pdf",height=25,width=25)
#op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : aphid count","\n")
#for(i in splist){
#  cat("sp=",i,"\n")
#  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
#  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
#                        numsurrog=numsurrog,
#                        ploton=T,
#                        corpres="kendall") 
#  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
# p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
#  skw_aphid_count_kendall$realskw[i]<-ans$realskw
#  skw_aphid_count_kendall$p_left[i]<-p_left
#  skw_aphid_count_kendall$p_right[i]<-p_right
#  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
#}
#par(op)
#dev.off()
#saveRDS(skw_aphid_count_kendall,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_kendall.RDS")
```

```{r skewness_aphidff_allsp_plot, echo=F, results="hide", cache=T, cache.extra=list(seed,data_aphid_ff,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

# For sp =12 and sp=16 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite,
# also it can't handle ties for "kendall" and code crashes
# you can see those msg by deleting results="hide" and warning=F option in r chunk

numsurrog<-10000

splist<-c(1:20)
skw_aphid_ff_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_spearman.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_spearman$realskw[i]<-ans$realskw
  skw_aphid_ff_spearman$p_left[i]<-p_left
  skw_aphid_ff_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_spearman,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_spearman.RDS")

#skw_aphid_ff_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
#colnames(skw_aphid_ff_kendall)<-c("realskw","p_left","p_right")
#rownames(skw_aphid_ff_kendall)<-paste("sp",splist,sep="")
#pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_kendall.pdf",height=25,width=25)
#op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : aphid ff","\n")
#for(i in splist){
#  cat("sp=",i,"\n")
#  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
#  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
#                        numsurrog=numsurrog,
#                        ploton=T,
#                        corpres="kendall") 
#  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
#  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
#  skw_aphid_ff_kendall$realskw[i]<-ans$realskw
#  skw_aphid_ff_kendall$p_left[i]<-p_left
#  skw_aphid_ff_kendall$p_right[i]<-p_right
#  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
#}
#par(op)
#dev.off()
#saveRDS(skw_aphid_ff_kendall,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_kendall.RDS")
```

```{r skewness_plankton_allsp_plot, echo=F, results="hide", cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

# There is no error msg or warning coming from ncsurrog : ncov semidefinite matrix for any species with spearman or kendall preserving surrogates.
# But there may be error handling ties with "kendall"
# So,for safety, now we will only analyze with "spearman"

splist<-c(1:22)
skw_plankton_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_plankton_spearman)<-c("realskw","p_left","p_right")
rownames(skw_plankton_spearman)<-paste("sp",splist,sep="")
#skw_plankton_kendall<-skw_plankton_spearman
pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_spearman.pdf",height=30,width=30)
op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for spearman preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_spearman$realskw[i]<-ans$realskw
  skw_plankton_spearman$p_left[i]<-p_left
  skw_plankton_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_spearman,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_spearman.RDS")

#pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_kendall.pdf",height=30,width=30)
#op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : pns","\n")
#for(i in splist){
  #cat("sp=",i,"\n")
 # loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
#  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
#                        numsurrog=numsurrog,
#                        ploton=T,
#                        corpres="kendall") 
#  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
#  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
#  skw_plankton_kendall$realskw[i]<-ans$realskw
#  skw_plankton_kendall$p_left[i]<-p_left
#  skw_plankton_kendall$p_right[i]<-p_right
#  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
#}
#par(op)
#dev.off()
#saveRDS(skw_plankton_kendall,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_kendall.RDS")
```

>>>>

 The Great Miami Wetland Mitigation Bank  was at $36^{\circ}46^{'}51^{''}$ N, $84^{\circ}20^{'}26^{''}$ W) in Trotwood, Montgomery County, Ohio. Additional information on the history of the site and soil types is detailed in @Jarecke2016. Briefly, the closed static flux chamber method was used [@Holland1999] to measure $CH_{4}$ fluxes at 28 locations across a hydrologic gradient (upland to seasonal wetland) at daily to weekly interval from September 2015 to September 2016. **See and** @smyth2019using, **pending for
additional details???** on greenhouse gas flux methods for this site. We considered 13 locations that had at least 50 dates data.

@@
